\section{Target Blacklist Selection}

%A large scale breadth study to get a sense for which are the most popular
%free blacklists that are being used.
By far we have demonstrated the methodology and the requirements for selecting
measurement candidates. One question we have not addressed is what IP blacklists
we choose to test against. Section~\ref{sec:methodology} described the criteria
for sampling blacklist IPs from a given blacklist, but we still need to pick
the blacklist in the first place.

Since we do not have access to commercial IP blacklists, we choose our
candidates from public blacklists. The FireHOL IP blacklist collection, as we
mentioned earlier, aggregates a comprehensive list of public IP blacklists, so
we will conduct our measurement against these blacklists. However, it would be
too expensive for us to test against all these blacklists. Furthermore, some
blacklists might not be used by many hosts to block traffic, which then would
not give us much insight about blocking behavior on the Internet.

In this paper, we would like choose the most popular public IP blacklists,
and conduct our measurement and analysis in detail regarding these
blacklists. To choose the most popular blacklist, we conduct our measurement
over 61 public IP blacklists from the FireHOL collection, and for each
blacklist, we sample 5 IPs from that list using the criteria specified
before. Here we only test 61 blacklists since some lists are obsolete now,
and we only focus on the currently active blacklists. 5 sample points from
one list is not a strong enough indicator to conclude whether a host is using
that blacklist or not, but the goal of the experiment is not to identify the
exact hosts that use a blacklist. Rather, it is to get a close estimation so
we can figure out the most widely used blacklists for later measurements. We
repeat this experiment twice and select the top {\blacklistnum} blacklists
\footnote{We initially selected 10 blacklists, but one blacklist, abuse.ch
Ransomware List, was discontinued by the provider during our experiments, so
we discard that list.}, as listed in Table~\ref{tab:target-blacklists}.

\begin{table}
\centering
\caption{Selected {\blacklistnum} popular public IP blacklist. {\ettor} here is
the combination of three Tor blacklists, as they are having mostly the same
content.}
\label{tab:target-blacklists}
\footnotesize
\begin{tabular}{l r}
 \toprule
 Blacklist   & \quad\quad\quad\quad\quad Average Number of IPs \\
 \midrule
 \textbf{\spamhausdrop}                 & $\sim$ 20,000,000       \\
    \multicolumn{2}{l}{    Spamhaus Don't Route Or Peer Lists}  \\
    %\hspace{0.2cm}    https://www.spamhaus.org/drop/drop.txt \\

 \textbf{\spamhausedrop}                &  $\sim$ 900,000          \\
    \multicolumn{2}{l}{    An extension of the Spamhaus DROP list} \\
    %\hspace{0.2cm}    https://www.spamhaus.org/drop/edrop.txt \\

 \textbf{\dshieldtop}                   &  5,120            \\
    \multicolumn{2}{l}{    DShield.org recommended top 20 /24s to block} \\
    %\hspace{0.2cm}    https://www.dshield.org/block.txt \\

%\textbf{\ciarmy}                       & 15,000            \\
    %\multicolumn{2}{l}{    Collective Intelligence Network Security(CINS) blacklist} \\
    %\hspace{0.2cm}    http://www.ciarmy.com/list/ci-badguys.txt \\

 \textbf{\etcompromised}                & $\sim$ 400               \\
    \multicolumn{2}{l}{    EmergingThreats.net recorded compromised hosts} \\
    %\multicolumn{2}{l}{\hspace{0.2cm} https://rules.emergingthreats.net/blockrules/compromised-ips.txt} \\

 \textbf{\snortfilter}                  & $\sim$ 1,500             \\
    \multicolumn{2}{l}{    labs.snort.org supplied IP blacklist}  \\
    %\hspace{0.2cm}    http://labs.snort.org/feeds/ip-filter.blf \\

 \textbf{\bdsatif}                      & $\sim$ 6,000             \\
    \multicolumn{2}{l}{    Binary Defense System ban list} \\
    %\hspace{0.2cm}    https://www.binarydefense.com/banlist.txt \\

 \textbf{\feodo}                        & $\sim$ 700              \\
    \multicolumn{2}{l}{    Abuse.ch Feodo tracking list}  \\
    %\hspace{0.2cm}    https://feodotracker.abuse.ch/downloads/ipblocklist.txt \\

 \textbf{\blocklistde}                  & $\sim$ 30,000           \\
    \multicolumn{2}{l}{    Blocklist.de blacklist IPs} \\
    %\hspace{0.2cm}    http://lists.blocklist.de/lists/all.txt\\

 \textbf{\ettor}                        & $\sim$ 6,000             \\
       \multicolumn{2}{l}{ IPs that are belong to Tor network(not just exits node)}  \\
       %\multicolumn{2}{l}{\hspace{0.2cm}    https://rules.emergingthreats.net/blockrules/emerging-tor.rules} \\
 \bottomrule
\end{tabular}
\end{table}
