\section{Discussion}


\subsection{Limitation}
%Our measurement took the first step to understand how threat intelligence
%blacklists are used on the Internet.
Our experiment took the first to unveil how threat intelligence blacklists are
used on the Internet, by measuring over 220K hosts on the Internet. One
limitation of our measurement, however, is the hosts we selected. We select
these hosts primarily based on the present of IP ID side channel, and low
network traffic. This might affect our candidate selection, provide us a biased
set of sample set. We provide a lower bound for the threat intelligence usage
online.

Another limitation is our limited access to the commercial threat intelligence
products. All the experiment in this paper is conducted with public threat
intelligence feeds. As we see from Section~\ref{sec:partial-blocking} and
Section~\ref{sec:large-scale}, the potential number of hosts that are using
some threat intelligence products is much higher. In this paper, we took the
best effort to peer into the commercial space, relying on the fact that some
commercial products share content with public feeds. Future work should explore
more the commercial threat intelligence.


\subsection{Future Work}
Our work try to understand the usage of threat intelligence products. We utilize
the IP ID side channel and measured one specific type of usage: network layer
traffic blocking. But as we mentioned earlier, there are many different ways
people can use the threat intelligence, future work should focusing more on
unveiling other type of usage, for example, application layer access deny.

Another thing regarding the IP ID side channel is that although the global
shared IP ID counter is regarded as old implemention, and more recent system
have switched to more modern implementions. But as pointed out by~\cite{klein2019ip},
even the most recent IP ID implementation still consist of exploitable side
channels. Future work could explore the possibility to using these side channels,
to create more vantage points for this type of measurement.
