\documentclass[12pt]{ucsddissertation}
% mathptmx is a Times Roman look-alike (don't use the times package)
% It isn't clear if Times is required. The OGS manual lists several
% "standard fonts" but never says they need to be used.
\usepackage{mathptmx}
\usepackage[NoDate]{currvita}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage[breaklinks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{graphicx}
\AtBeginDocument{%
	\settowidth\cvlabelwidth{\cvlabelfont 0000--0000}%
}
\input{preamble.tex}
\input{datadef.tex}

% OGS recommends increasing the margins slightly.
\increasemargins{.1in}

% These are just for testing/examples, delete them
\usepackage{trace}
%\usepackage{showframe} % This package was just to see page margins
\usepackage[english]{babel}
\usepackage{blindtext}
\overfullrule5pt
% ---

% Required information
\title{Understand Threat Intelligence: Data, Operation and Threat Landscape}
\author{Guo Li}
\degree{Computer Science}{Doctor of Philosophy}
% Each member of the committee should be listed as Professor Foo Bar.
% If Professor is not the correct title for one, then titles should be
% omitted entirely.
\cochair{Professor Stefan Savage}
\cochair{Professor Kirill Levchenko}
% Your committee members (other than the chairs) must be in alphabetical order
\committee{Professor Geoffrey M. Voelker}
\committee{Professor Deian Stefan}
\committee{Professor Xinyu Zhang}
\degreeyear{2020}

% Start the document
\begin{document}
% Begin with frontmatter and so forth
\frontmatter
\maketitle
\makecopyright
\makesignature
% Optional
\begin{dedication}
\setsinglespacing
\raggedright % It would be better to use \RaggedRight from ragged2e
\parindent0pt\parskip\baselineskip
In recognition of reading this manual before beginning to format the
doctoral dissertation or master's thesis; for following the
instructions written herein; for consulting with OGS Academic Affairs
Advisers; and for not relying on other completed manuscripts, this
manual is dedicated to all graduate students about to complete the
doctoral dissertation or master's thesis.

In recognition that this is my one chance to use whichever
justification, spacing, writing style, text size, and/or textfont that
I want to while still keeping my headings and margins consistent.
\end{dedication}
% Optional
\begin{epigraph}
\vskip0pt plus.5fil
\setsinglespacing
{\flushright
True ease in writing comes from art, not chance,\\
As those move easiest who have learn'd to dance.\\
'T is not enough to no harshness gives offence,---\\
The sound must seem an echo to the sense.

\vskip\baselineskip
\textit{Alexander Pope}\par}
\vfil
\begin{center}
You write with ease to show your breeding,\\
But easy writing's curst hard reading.

\vskip\baselineskip
\textit{Richard Brinsley Sheridan}
\end{center}
\vfil
\noindent Writing, at its best, is a lonely life. Organizations for
writers palliate the writer's loneliness, but I doubt if they improve
his writing. He grows in public stature as he sheds his loneliness and
often his work deteriorates. For he does his work alone and if he is a
good enough writer he must face eternity, or the lack of it, each day.

\vskip\baselineskip
\hskip0pt plus1fil\textit{Ernest Hemingway}\hskip0pt plus4fil\null

\vfil
\end{epigraph}

% Next comes the table of contents, list of figures, list of tables,
% etc. If you have code listings, you can use \listoflistings (or
% \lstlistoflistings) to have it be produced here as well. Same with
% \listofalgorithms.
\tableofcontents
\listoffigures
\listoftables

% Preface
\begin{preface}
Almost nothing is said in the manual about the preface. There is no
indication about how it is to be typeset. Given that, one is forced to
simply typeset it and hope it is accepted. It is, however, optional
and may be omitted.
\end{preface}

\input{acknowledgement.tex}

% Stupid vita goes next
\begin{vita}
\noindent
\begin{cv}{}
\begin{cvlist}{}
\item[2014] Bachelor of Science, Peking University
\item[2014--2020] Research Assistant, University of California, San Diego
\item[2017] Master of Science in Computer Science, University of California, San Diego
\item[2020] Doctor of Philosophy in Computer Science, University of California, San Diego
\end{cvlist}
\end{cv}
\end{vita}


% Put your maximum 350 word abstract here.
\input{abstract.tex}

% This is where the main body of your dissertation goes!
\mainmatter

% Optional Introduction
\input{introduction.tex}
\input{background/background.tex}
\input{data_character/data_character.tex}
\input{data_usage/data_usage.tex}
\input{conclusion.tex}
%\appendix
%\Blinddocument

% Stuff at the end of the dissertation goes in the back matter
\backmatter
\bibliographystyle{plain} % Or whatever style you want like plainnat
\bibliography{local,sysnet,background}

\end{document}
