\section{IP Threat Intelligence}
\label{sec:ip-analysis}

One of the most common forms of \ti\ are feeds of IP addresses considered malicious,
suspicious, or otherwise untrustworthy. This type of threat intelligence dates back
at least to the early spam and intrusion detection blacklists, many of which are
still active today such as SpamhausSBL~\cite{SpamhausSBL}, CBL~\cite{CBL} and
SORBS~\cite{SORBS}. Here, we apply the metrics described above to quantify the
differences between \numipfeeds\ different IP address \ti\ feeds.
%The overview of the these feeds is summarized in Table~\ref{tab:volume-overview-1}.


\subsection{Feed Categorization}
IP address \ti\ feeds have different meanings, and, therefore, purposes. To
meaningfully compare feeds to each other, we first group feeds into
\emph{categories} of feeds whose indicators have the same intended meaning.
Unfortunately, there is no standard or widely accepted taxonomy of IP \ti\ feeds.
To group feeds into semantic categories, we use metadata associated with the
feed as well as descriptions of the feed provided by the producer, as described below.

\emphpar{Metadata} Some feeds provide category information with each indicator as
metadata. More specifically, all of the {Paid Aggregator} feeds, {\feedalienvault}
and {\feedetiprep} include this category metadata. In this case, we use its pre-assigned
category in the feed. Facebook ThreatExchange feeds do not include category
information in the metadata, but instead provide a descriptive phrase with each indicator.
We then derive its category based on the description.

\emphpar{Feed description} For feeds without metadata, we rely on online descriptions
of each feed, where available, to determine its semantic category. For example, the
website of feed {\feednothink}~\cite{Nothink} describes that the feed reports brute-force
login attempts on its corresponding honeypot, which indicates the feed belongs to
brute-force category.

We grouped our IP feeds into categories derived from the information
above. In this work, we analyze six of the most prominent categories:
%, listed below.
%
\begin{categorylist}\small
\item[Scan] Hosts doing port or vulnerability scans.
\item[Brute-force] Hosts making brute force login attempts.
\item[Malware] Malware C\&C and distribution servers.
\item[Exploit] Hosts trying to remotely exploit vulnerabilities.
\item[Botnet] Compromised hosts belonging to a botnet.
\item[Spam] Hosts that sent spam or should not originate email.
\end{categorylist}
%
Table~\ref{tab:volume-overview-1} lists the feeds, grouped by category, used in the
rest of this section. The symbols \snapfeedsym\ and \deltafeedsym\ before the feed
name indicate whether the feed is a snapshot feed or an event feed, respectively
(see Section~\ref{sec:feed-structure}).
All data was collected during our measurement period,
\veryemph{December 1st, 2017} to \veryemph{July 20th, 2018}. Note that a few
feeds, like {\feedetiprep}, appear in multiple categories. In these feeds, indicators
are associated with different categories via attached metadata. We split these feeds
into multiple virtual feeds each containing indicators belonging to the same category.

\input{content/ip-volume}
\input{content/ip-overlap}
\input{content/ip-unique}
\input{content/ip-timing}
\input{content/ip-accuracy}
\input{content/ip-compl}



%\subsection{Inter-Category}
%\input{content/inter_category.tex}
%Pick three or four categories of feeds, analyze their \textit{overlap}, \textit{uniquness} and \textit{time attributes}
%\label{sec:analysis}
%\input{content/analysis_scan.tex}
