\subsection{Exclusive Contribution}
\label{sec:ip-unique}

Exclusive contribution represents the number of indicators in a feed that are in no other feeds. I calculate each feed's exclusive contribution among all the feeds in the same category, emphasizing their uniqueness regarding the scope of data they claim to report. Each feed's exclusive contribution is presented in Table~\ref{tab:volume-overview-1} in column \emph{Exclusive}, calculated based on its volume.

\finding\ As I already observed in Section~\ref{sec:ip-overlap}, botnet, exploit and spam feeds have relatively low pairwise intersections. Consequently, the feeds in these four categories have high exclusive contribution rates in general: the median exclusive contribution rates of these four categories are 90.9\%, 97.5\% and 90.5\%, respectively. The malware category has a low median exclusive rate, since multiple small feeds have non-trivial intersection with the largest feed {\feedetiprep}, but the two largest feeds in malware both have a exclusive rate over 99\%. Scan and brute-force feeds have more intersection within its category, and their exclusive rates are lower: 62.0\% median rate in scan and 62.7\% in brute-force, and the top two largest feeds in both categories have an exclusive rate below 85\%.

If one assumes a process where a feed is more likely to have popular elements, then smaller feeds would be subsumed by larger feeds. Yet, for some small feeds like {\feedmalcode} in the malware and {\feedTSHoneypot} in the botnet categories, even though they are several orders of magnitude smaller than the largest feeds in their categories, a significant proportion of their indicators is still unique to the feed. When I aggregate the data in each category, 73\% of all scan feed indicators are unique to a single feed and 88\% of brute force feed indicators are unique to one feed. For other categories, over 97\% of elements in the category are unique to a single feed. This result agrees with previous work that most data in threat intelligence feeds is unique~\cite{metcalf2015blacklist,thomas2016abuse}.